---
title: "hostsynch"
format: pdf
editor: visual
---

## Methods

For host species $i$, let us assume that the recruitment of new susceptibles ($B$) is described with the Ricker equation:

\begin{equation}
B(N_{i,t}) = N_{i,t} exp(r_{i,t}  (\frac{1 - N_{i,t}}{K_i})).
\label{ricker_discrete_model}
\end{equation}

Here, $r_t$ is the intrinsic growth rate and is time-dependent; $K$ is the specices' carrying capacity. Including infection:

\begin{equation}
S_{i,t+1} = N_{i,t} exp(r_t  (\frac{1 - N_{i,t}}{K_i})) -
\sum_{j=1}^{n} \beta_{j} S_{i,t} I_{j,t} - \mu_i S_{i,t},
\end{equation}

\noindent the susceptible individuals can be infected by members of its own species as well as by members of other species. The transmission coefficient $\beta$ can be unique to the species and will determine the species' competence. The total number of new infections is: $\sum_{j=1}^{n} \beta_{j} S_{i,t} I_{j,t}$.

As the susceptibles enter into the infected class: \begin{equation}
I_{i,t+1} =\sum_{j=1}^{n} \beta_{j} S_{i,t} I_{j,t} - (\gamma_i + \mu_i) I_{i,t},
\end{equation}

\noindent where individuals recover at the rate of $\gamma$. When individuals recover, we have:

\begin{equation}
R_{i,t+1} = \gamma_i I_{i,t} -  \mu_i R_{i,t},
\end{equation}

fully-recovered hosts cannot get reinfected.

```{r}

ricker_SIR_model <- function(r = 0.5){}


```

\subsection{Varying temporal fluctuations}

We model the intrinsic growth rate of each species as being seasonal:

\begin{equation}
r_{(i,t)} = r_0 + sin (wt + o_i) + \epsilon_t,
\end{equation}

For our mathematical model, we assume the following:

1.  The

```{r}
n_sp = 100

```

## 
